Storing messages with multipartite neural cliques

### 2014-07-09 Articles/article.tex
La personne ayant codée seq en R mérite le pire des sorts ! 1:0 = c(1,0), que c'est brillant !
Ajout formule théorique.
..;
...
....

		To fully exploit the local regularity of the code (constant weight of $a$), we make a small modification the classic retrieving rule	by keeping activated all neurons that achieve a score equal or greater than the score appearing in $a$-th position in the ordered array of scores.

		$a$-rank

		Although it is a less biologically plausible rule, it has the same algorithmic complexity, since selecting the $a$-th element in an array of $n$ elements is $O(n)$ in complexity.

		Intuitively the choice $w = a$ is optimal (it it is the most natural with $w = 1$)

		\begin{algorithm}
		\caption{$a$-sum of sum \label{asumsum}}

		\begin{algorithmic}[1]
		\Require{i}
		\Procedure{Euclid}{$a,b$}
		\Statex
		\While{$s < I$}
		\Let{a}{b}
		\If {$i\ge maxval$}
   	 	\State $i\gets 0$
		\Else
    		\If {$i+k\leq maxval$}
        	\State $i\gets i+k$ \Comment{$\oplus$: bitwise exclusive-or}
    		\EndIf
		\EndIf
		\EndWhile
		\EndProcedure
		\end{algorithmic}
		\end{algorithm}

@@

	%edge : $(i, j)$

@@

	% À corriger avec sommes multiparties
	%$P(\mbox{no other vertex activated in this cluster})= \sum_{n_0 = 1}^{a (c - c_e)} P(n_{v_c} \ge n_0)^a \left [ \sum_{x = 0}^{n_0 - 1} P(n_v = x) \right]^{l-a}$

	%$P(\mbox{no other vertex activated in any cluster})=  \left ( \sum_{n_0 = 1}^{a ( c - c_e)} P(n_{v_c} \ge n_0)^a \left [ \sum_{x = 0}^{n_0 - 1} P(n_v = x) \right]^{l-a } \right)^{c_e}$

	Sans tenir compte du choix au hasard si plus sont activés.

@@

	$P(\mbox{no other vertex activated in this cluster})= \sum_{n = 1}^{a (c - c_e)} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{v_c} = n)^k P(n_{v_c} > n)^{a-k} \right ] \left [ \sum_{x = 0}^{n - 1} P(n_v = x) \right]^{l-a }$

@@

	\newpage
	%$\,$
	%\newpage
	\begin{figure}

		\includegraphics[scale=0.55]{Courbes/5portant_psi_c8l256e4}
		\caption{Comparison of efficiencies between different number of activities per cluster :  8 clusters, 256 neurons per cluster, 1000 sampled messages, pools of 5 networks \label{comppsi}}
	\end{figure}

@@

>>>>

		To fully exploit the local regularity of the code (constant weight of $a$), we make a small modification the classic retrieving rule	by keeping activated all neurons that achieve a score equal or greater than the score appearing in $w$-th position in the ordered array of scores (where $w$ is a positive integer parameter)

		%$a$-rank

		Although it is a less biologically plausible rule, it has the same algorithmic complexity, since selecting the $w$-th element in an array of $n$ elements is $O(n)$ in complexity.

		Intuitively the choice $w = a$ is optimal (it it is the most natural with $w = 1$).

		\begin{algorithm}
		\caption{$w$-sum of sum \label{asumsum}}

		\begin{algorithmic}[1]
		\Require{$v$ a binary array of length $n = c\cdot l$}
		\Procedure{Sum of sum}{$v, w$}
		%\Statex
		\While{$s < I$}
		\Let{a}{b}
		\If {$i\ge maxval$}
   	 	\State $i\gets 0$
		\Else
    		\If {$i+k\leq maxval$}
        	\State $i\gets i+k$ \Comment{$\oplus$: bitwise exclusive-or}
    		\EndIf
		\EndIf
		\EndWhile
		\EndProcedure
		\end{algorithmic}
		\end{algorithm}

@@

	%edge : $(i, j)$
	Suppose we are trying to recover a message where $c_e$ clusters have been erased.

@@

	% À corriger avec sommes multiparties
	$P(\mbox{no other vertex activated in this cluster})= \sum_{n_0 = 1}^{a (c - c_e)} P(n_{v_c} \ge n_0)^a \left [ \sum_{x = 0}^{n_0 - 1} P(n_v = x) \right]^{l-a}$

	% Approx : ?! $P(\mbox{no other vertex activated in any cluster})=  \left ( \sum_{n_0 = 1}^{a ( c - c_e)} P(n_{v_c} \ge n_0)^a \left [ \sum_{x = 0}^{n_0 - 1} P(n_v = x) \right]^{l-a } \right)^{c_e}$

	Sans tenir compte du choix au hasard si plus sont activés. Pour une itération $\gamma = \infty$. Pour plusieurs $\gamma = 1$.

@@

	$P(\mbox{no other vertex activated in this cluster})= \sum_{n = 1}^{a (c - c_e)} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{v_c} = n)^k P(n_{v_c} > n)^{a-k} \right ] P(n_v < n)^{l-a}$%[ \sum_{x = 0}^{n - 1} P(n_v = x) \right]^{l-a }$

@@

	\newpage
	%$\,$
	%\newpage
	\begin{figure}[!htb]
		\includegraphics[width=8.5cm]{Courbes/thpsi_c8l256e4}
		\caption{2 activities per cluster, 8 clusters, 256 neurons per cluster, 4 erasures, each point is the mean of 10 networks with 1000 sampled messages, analytical result in continuous black}
		\label{psith}
	\end{figure}

	\begin{figure}

		\includegraphics[scale=0.50]{Courbes/5portant_psi_c8l256e4}
		\caption{Comparison of efficiencies between different number of activities per cluster :  8 clusters, 256 neurons per cluster, 1000 sampled messages, pools of 5 networks \label{comppsi}}
	\end{figure}

@@

	\section{Maximum theoretical efficiency}
		\begin{align*}
			H(M) \approx m c \log_2 {l \choose a}\\
			d = 1 - \left (1- \left(\frac{a}{l}\right)^2 \right)^m\\
			m \sim \frac{\log_2(1-d)}{\log_2(1-(\frac{a}{l})^2)} \sim - \frac{l^2 \log_2(1-d) \log 2}{a^2}\\
			\log_2 {l \choose a} = k c\\
			\eta \sim c \log_2 {l \choose a} \log2(1-d) \sim \frac{k c^2 \log_2(1-d)\log 2}{a^2 {c \choose 2}}\\
			\eta \sim - 2 k  \log_2 ((1-d)a^{-2}\log 2\\
			P_{\exists e} \le {l \choose a}^c d^{a^2 {c \choose 2}} = 2^{c \log_ 2 {l \choose a} + a^2 {c \choose 2 }\log_2(d)} \approx 2^{c^2(k + \frac{a^2}{2} \log_2 (d))}\\
			k^* = -\frac{a^2}{2} \log_2 (d)\\
			\eta \sim \log_2 d \log_2 (1-d) \log 2\\
			\eta_{max} \rightarrow \log 2
		\end{align*}
